Toxic Code Snippets on Stack Overflow

### 2018-05-09 cloverflow-tse/cover_letter/cover_letter.tex
Updated the outdated vs. GitHub results and updated the software license auditing survey results.

\begin{enumerate}
	\item We understand the concern of finding real evidence to support that code snippets on Stack Overflow do appear in software projects. Hence, we have performed a study of code clone detection between our reported outdated code fragments on Stack Overflow and 131,307 most starred GitHub projects. We found that there are xxx clone instances of xxx outdated Stack Overflow code snippets appearing in xx GitHub projects. Interestingly, we discovered that the buggy version of the \texttt{humanReadableInt()} method from Hadoop appears in two popular Java projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854 stars and 1,946 forks). Unfortunately, due to the lack of evidence, we could not explain how this method, which is exactly the same as the toxic code snippet we found on Stack Overflow, appear in the two projects. It is possible that the developers retrieved them from Stack Overflow, other websites, or from Hadoop code base directly.

	Nevertheless, we decided to report the developers of the two projects regarding the issue. We created a bug report for each project (deeplearning4j \#4694\footnote{deeplearning4j bug report: \url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and HIVE-18929\footnote{Apache Hive bug report: \url{ https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the developers of the projects by describing the problem of race condition in the outdated version of \texttt{humanReadableInt()} method and proposed a fix by using the newest version of the method in Hadoop. The issue has been fixed in deeplearning4j. The developers of deeplearning4j agreed that the method was problematic and they decided to implement their own fix due to a concern of a potential software licensing conflict caused by copying the fix directly from Hadoop code base. On the other hand, the bug report in Apache Hive is still unfixed.
	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub. However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information. Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets because ... developers in the future.}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets because ... developers in the future.}''.
\end{enumerate}

@@

We adopted non-probability convenient sampling to invite participants for this survey. Participation in the survey requires experience of visiting Stack Overflow for solving programming tasks at least once. The participants were invited to take the survey via various channels: social media post (Facebook), Thailand's popular technology news and media community in Thailand called \texttt{blognone.com}, the University of Molise in Italy where the third author works, \texttt{comp.lang.java.programmer} group and the Software Engineering Facebook page. We received answers from 89 participants. Two participants never copy code from Stack Overflow so we analysed the answers of the remaining 87 participants. The key findings are as follows.

@@

@@

In addition, we also performed a small survey of software auditing platforms/services including:~\FIXME{Blackduck OpenHub, foo, and bar} and found that, while they check for code copied from open source projects and analyse their license compatibility, none of them offers the checking for cloned code from Stack Overflow. So, our proposed service will be useful as an add-on check for code copying from Stack Overflow and their license implications.

@@

You are right. We mainly study the online code clones and established their existence. However, we coined the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning. 
We updated the Introduction to be clearer on this point~\FIXME{to do}.
%Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.

@@

We expanded the analysis of the survey results \FIXME{Where? and How?} and now moved them to RQ1 to better link with the motivation. We also added results of another survey, the Stack Overflow visitor survey, to understand the awareness of the developers who copied code snippets from Stack Overflow regarding outdated and license-incompatible code.

>>>>

\begin{enumerate}
	\item We understand the concern of finding real evidence to support that code snippets on Stack Overflow do appear in software projects. Hence, we have performed a study of code clone detection between our reported outdated code fragments on Stack Overflow and 131,703 GitHub projects ranging from 29,465 stars to 1 star. We selected SourcererCC with 80\% similarity for this experiment and detected clones between the 101 outdated code snippets and the retrieved GitHub data set. We relied on SourcererCC because it could scale to a large-scale data set, while Simian could not. We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them. Out of the 102 cloned snippets, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly matched (they contained additional code modifications made by the projects' developers). Lastly, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.

	Among the exact-copy of 47 outdated cloned snippets, there were only two cloned snippets that gave attributions to Stack Overflow. However, the attributions pointed to different posts that the ones we found the outdated code, but containing the same code in the answers. The other 32 cloned snippets were very likely to be a file-level clone from its original projects based on their license header and the Javadoc comments. Lastly, the remaining 13 cloned snippets did not have any hints or evidence of copying.
	Interestingly, we discovered that the buggy version of the \texttt{humanReadableInt()} method from Hadoop appears in two popular Java projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854 stars and 1,946 forks). Due to the lack of evidence, we could not conclude how this method, which is exactly the same as the toxic code snippet we found on Stack Overflow, appear in the two projects. It is possible that the developers retrieved them from Stack Overflow, other websites, or from Hadoop code base directly.  
	Nevertheless, we decided to report the developers of the two projects regarding the issue. We created a bug report for each project (deeplearning4j \#4694\footnote{deeplearning4j bug report: \url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and HIVE-18929\footnote{Apache Hive bug report: \url{ https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the developers of the projects by describing the problem of race condition in the outdated version of \texttt{humanReadableInt()} method and proposed a fix by using the newest version of the method in Hadoop. The issue has been fixed in deeplearning4j. The developers of deeplearning4j agreed that the method was problematic and they decided to implement their own fix due to a concern of a potential software licensing conflict caused by copying the fix directly from Hadoop code base. On the other hand, the bug report in Apache Hive is still unfixed.
	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub. However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information. Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets because ... developers in the future.}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets because ... developers in the future.}''.
\end{enumerate}

@@

tho
Thailand's popular technology news and media community in Thailand called
\texttt{blognone.com}, the University of Molise in Italy where the third author
works, \texttt{comp.lang.java.programmer} group and the Software Engineering
Facebook page. We received answers from 89 participants. Two participants never
copy code from Stack Overflow so we analysed the answers of the remaining 87
participants. The key findings are as follows.

@@

The visitors survey confirms the findings from the previous studies that Stack
Overflow code snippets can be problematic~\citep{Zhang2018,Acar2016,An2017}. Sixty-six
percent of the visitors experienced a problem from reusing Stack Overflow code
snippets ranging from incorrect solutions, outdated solutions, mismatched
solutions, to buggy code. Although they are aware of the problems, half of them
(56\%) never reports back to the Stack Overflow discussions. On the other hand,
the visitors rarely give attributions to Stack Overflow when they reuse code
snippets from the website, similar to the findings reported
by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
license, and more than half of them never check for license compatibility when
reusing Stack Overflow code snippets. We also found that 9\% of the participants
encountered legal issues by copying code from Stack Overflow. To the best of our
knowledge, a study of legal problems from reusing Stack Overflow code snippets
has never been done before and will be our future work.

@@

In addition, we also performed a study of two open source software auditing platforms/services:~BlackDuck Software\footnote{https://www.blackducksoftware.com} and nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from their report~\citep{CORSI2017} that while they check for code copied from open source projects including GitHub and Stack Overflow and analyse their license compatibility with their customer software, the BlackDuck auditing system will treat the code snippets on Stack Overflow as having ``unknown'' license because it does not know the original license of Stack Overflow code snippets. For nexB, their product does not mention checking of reused source code from Stack Overflow. So, our proposed service, which can offer more precise licensing information of Stack Overflow code snippets, will be useful as an add-on license check for code copying from Stack Overflow.

@@

You are right. We mainly study the online code clones and established their existence. However, we used the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning. 
Moreover, the term code cloning is not well known outside the code cloning community, so we decided not to use the term in the title.

We also updated the Introduction to state that the dominant topic is about online code clones~\FIXME{to do}.
%Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.

@@

We moved them to RQ1 to better link with the motivation. We also expanded the findings to include another survey, the Stack Overflow visitor survey, in order to understand the awareness of the developers on both sides: the answerers and the visitors (i.e.~information seekers). We asked the visitors their experience regarding outdated and license-incompatible code caused by copying and reusing code snippets from Stack Overflow.
